A Fast Unified Model for Parsing and Sentence Understanding

### 2016-06-01 writing/hard_stack_paper/paper.tex
Add new NFS grant to acknowledgements

We acknowledge financial support from a Google Faculty Research Award, the Stanford Data Science Initiative, and the National Science Foundation under grant no.~BCS 1456077. Some of the Tesla K40s used for this research were donated by the NVIDIA Corporation. We also thank Kelvin Gu, Noah Goodman, and many others in the Stanford NLP group for helpful comments.

>>>>

We acknowledge financial support from a Google Faculty Research Award, the Stanford Data Science Initiative, and the National Science Foundation under grant nos.~BCS 1456077 and IIS 1514268. Some of the Tesla K40s used for this research were donated by the NVIDIA Corporation. We also thank Kelvin Gu, Noah Goodman, and many others in the Stanford NLP group for helpful comments.
